The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex

The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}.  When
set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.

If $f = x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is simply $\min \{ 1/a_1, \ldots, 1/a_n \}$.  When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.  We note that algorithms for computing $F$-pure thresholds of binomials in certain special characteristics appear in \cite{ShibutaTakagiLCThresholds}.

>>>>

The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}.  When
set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order. 
When $f$ is a monomial, say, $x_1^{a_n}\cdots x_n^{a_n}$, then its $F$-pure threshold is quickly computed as the minimum among the $1/a_i$.
When $f$ is a a diagonal polynomial, a binomial, a form in two variables, 
algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold (cf. \cite{ShibutaTakagiLCThresholds}).
